---
title: "Simple document"
author: Alex Perry
date: July 2021
output: 
  html_document:
    toc: true # create table of contents
    toc_float: true #creates floating table of contents
    code_folding: hide # hides code chuncks
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

The code chunk below creates a datafraem and generates a plot.

## Data frame and plot

```{r plot_example, message = FALSE}
library(tidyverse)

plot_df = tibble(
  x = rnorm(500, mean = 2, sd = 4),
  y = 3 - 4.2 * x + rnorm(500)
  
)

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

This plot is really great!! It shows a linear relationship just as expected.


The data frame has `r nrow(plot_df)` rows.

# Section 3

Here is a list:

* This is my first list item
* Lists need at least two items
  * this list has a sub item
* Third list item

Col 1 | Col 2
------|--------
a     |    b
c     |    c
d     |    e

> This is a block quote









